Data Preparation

### 2019-01-09 Data Preparation.Rmd
Combining AoD met from ILOs, and from assessment

>>>>

### Combining AoD from ILOs and from assessments
Finally, we can use a `rbind` to combine the two tibbles `d_AoD_ILO` and `d_AoD_assessment`. We also use `unique` in case a course covers an AoD with both its ILOS and its assessments.
```{r}
d_AoD <- rbind(d_AoD_ILO, d_AoD_assessment) %>%
  unique %>%
  arrange(Code)
print(d_AoD)
```
